% \input{ICT_Frontiers_rev202001.tex}
\documentclass[utf8]{article}
% \usepackage{RevisionToolsByAcer}
% \ProvidesPackage{RevisionToolsByAcer}
% \documentclass[utf8]{article}
% \ProvidesPackage{RevisionToolsByAcer}
%% Language and font encoding
\usepackage[english]{babel}
\usepackage[round, sort]{natbib}
\usepackage[T1]{fontenc}



% ============================ Sourcing main file ============================ %
\usepackage{xr}
\externaldocument{ICT_Frontiers_rev202001}
\usepackage{lineno}





% Sets page size and margins
% \usepackage[a4paper, top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=4cm]{geometry}
\usepackage[papersize={10in, 12in}, top=3cm,bottom=2cm,left=2in,right=2in,marginparwidth=1.8in]{geometry}
\usepackage{titlesec}
\usepackage[dvipsnames,table,xcdraw]{xcolor}
\usepackage[at]{easylist}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{authblk}
\usepackage{float}
\usepackage{tikz}
\usepackage[threshold=2, autopunct=true, autostyle=true]{csquotes}
\usepackage[colorinlistoftodos]{todonotes}


% =============================== Header style =============================== %
\titlelabel{}


% ============================================================================ %
%                               Macros from Acer                               %
% ============================================================================ %

		
% --------------------------------- Question --------------------------------- %	
\newcounter{cQuestion}[section]
\newenvironment{question}
    {\refstepcounter{cQuestion}\color{Blue}\noindent\newline Q\thecQuestion:}
    {~\newline}
    
% ------------------------------------ Ans ----------------------------------- %
\newenvironment{ans}  
    {\color{Black}\noindent A:}
    {~\newline}    
    
    
\newcommand{\QA}[2]{
    \begin{question}  
        #1
    \end{question}
        
    \begin{ans}  
        #2
    \end{ans}
}

% ---------------------------------- Revise ---------------------------------- %
% \Revise{Page}{original text}{revised text}
\newcommand{\revise}[3]{
	\newline
	\newline
    \noindent
    \textbf{Line #1:}
    \newline
    Original:\newline
    \textit{"#2"}
    \newline
    \newline
    Revised:\newline
    \textit{"#3"}\newline}

% ---------------------------------- Add New --------------------------------- %
% \addnew{line number}{text}
\newcommand{\addnew}[2]{\blockcquote{}{\textbf{Line #1:}~\newline\textit{"#2"}}
}

% ================================ Annotation ================================ %
\newcommand{\toWrite}[1]{\noindent
	\textcolor{Orange}{\textbf{[[ #1 ]]}}}


% =================================== Title ================================== %
\title{Response to Reviewers (Revision 1)}
\date{\today}
\author{} 



% =================================== Begin ================================== % 
\begin{document}

    \maketitle

    \section{Reply to Reviewer 1}
        \begin{question}
            Regarding the NTCI measure: \\\\
            a) Bertschinger et al. 2006 define informationally closed as $J_t(E\rightarrow Y) = 0$, but this is not a requirement for NTIC. Meaning, a positive NTIC measure does not entail that $J_t = 0$. $J_t = 0$ is only true if the NTIC is equal to $I(Y_{t+1}; E_t)$. In what sense does it correspond to non-trivial information closure then? (see also my concern \#2, maybe that is related) As defined in eq. 6 a video camera might have very high NTIC if it records a natural scene, even though it is in no way informationally closed from the environment.\\\\
            b) Is $NTIC_t$ state dependent or not? As capital letters are used I assume it is based on (conditional) mutual information measures across one time step but averaged over the possible states of the system at time t and t+1, so state distributions. But which distributions are used to compute $NTIC_t$? The stationary joint distribution of states at t and t+1? It cannot be just some observed measure, because then the level of consciousness would depend on how long the observation is. Moreover, if $NTIC_t$ is not state dependent, then the Reflex example on p. 10 is not intuitive. Because the system (brain) is the same and awake whether it behaves reflexively or not, so while the content may depend on the type of action, the $NTIC_t$ (level) would stay the same.              
        \end{question}
    
    	\begin{ans}
    		\newline
    		a) It is correct that the information flow term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$. However, in Definition 2, a C-process is informationally closed to the microscopic universe process $X$. This implies that the C-process is also informationally closed to any other coarse-graining of X, including E (see also our reply to Q2). Currently, we only consider that closed NTIC processes are C-processes. 
    		Regarding the video camera example, please see more discussion in our reply to your Q6. \\
    		
    		% Backup 2020/04/07 14:23
    		% ====================================
            % 		a) Considering Eq.\ref{eq:NTIC2}, it is true that the transfer entropy term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$. It is possible to have a high degree of NTIC when $J_t(E\rightarrow Y) > 0$, i.e. the process is not completely closed. We consider NTIC here as just the quantity defined in Eq.\ref{eq:NTIC2}.   \\

            %         Therefore, a conscious process does not have to be completely closed. 
            %         However, processes that manage to reduce the transfer entropy from the environment without reducing their mutual information with the environment achieve higher levels of consciousness. 
            %         Regarding the video camera example, please see more discussion in our reply to your Q6. \\
            % ====================================
            		
    		\noindent
    		b) It is correct that NTIC is not state-dependent. We agree that state-dependent measurements are essential to describing the dynamics of conscious experience. We are working on state-dependent formulations for the next version of the ICT. In contrast to the present version, this work involves point-wise informational measures and requires more space and discussion. We would therefore prefer to address the state-dependent version of ICT in future studies and keep the first version of our theory simple.
    		
    		Nevertheless, we appreciate that the reviewer’s raising of this issue, and have added a short paragraph about it:
    		
    	
	    	\addnew{\lineref{line:r1-state-dep}}{
	    		In this article, we do not use a state-dependent formulation of NTIC. However, we believe that state-dependent NTIC is essential to describing the dynamics of conscious experience. The next version of ICT therefore requires further research using point-wise informational measures to construct state-dependent NTIC.}
    	\end{ans}
        
       
        
        \begin{question}
            Hypothesis and Implication 3: Why is it crucial that there is an underlying $X$ with respect to which $Y$ is a C-process?     
        \end{question}
        
        \begin{ans}        	
            The C-processes are constructed to answer questions about the scale problem of consciousness. Their definition therefore states their relation to the microscopic scale $X$. 
            At the same time it would be possible to remove $X$ from the definition and instead require that $Y$ is informationally closed with respect to all other processes. In some cases such a definition would be more general than the present one for example when there is no final microscale but instead an infinite number of more and more microscopic scales. However, we find the use of an explicit microscale $X$ easier to understand and sufficient to communicate the idea. Note that closure with respect to $X$ (if it exists) implies closure with respect to every coarse-graining of $X$.   
            To grasp this, note that the information transfer from any coarse-graining (including $E$ and $S$) of $X$ to $Y$ must be lower than that from $X$ to $Y$, i.e. $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$. Accordingly, $Y$ is informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to $S, E$, and all other coarse-grainings of $X$.
        \end{ans}
        
        \begin{question}
            Does $Y$ being informationally closed with respect to $X$ imply that $Y$ is also informationally closed with respect to E, i.e. $J_t(E\rightarrow Y)= 0$? I don't think that could be true for the brain, or part of it really. My brain's next state, at whatever level, certainly depends to some degree on unpredictable sensory inputs from the environment. In the end, is $I(Y_{t+1}; E_t|Y_t) = 0$ required for consciousness or not? (see point 1a). In other points in the manuscript this does not seem required, e.g. p. 10 "If a process is not informationally closed, the degree of NTIC is low resulting in low or no consciousness".    
        \end{question}
        
        \begin{ans}
            Yes. As mentioned in our answer to Q2 $Y$ being informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to E, i.e. $J_t(E\rightarrow Y) = 0$.
            As explained in Question 1a, we currently only consider informationally closed processes as C-processes. The reviewer is also correct that our internal states depends to some degree on unpredictable sensory inputs from the environment. This results in some interesting predictions. For example, unpredicted sensory inputs may temporally break informational closure and ICT predicts that conscious agents may then lose consciousness for a short time. Unfortunately, referring to your Q1b, the current version of ICT does not include state-dependent IC and NTIC. Therefore, the current formulation of ICT cannot well describe the dynamics of conscious experience under unpredictable states. We expect that our next version of ICT will be better able to answer your question. 
            
            % it is not required for NTIC processes to be completely closed. The information transfer from $X$ to $Y$ $I(Y_{t+1}; X_t|Y_t)$ (if non-zero) serves as the upper bound of the information transfer from any other process to Y. So unpredictable sensory inputs will contribute to a positive information transfer. 
            % As mentioned before higher NTIC values are achieved when this information transfer can be reduced without reducing the mutual information between the sensory inputs and the next system state.
        \end{ans}
        

        \begin{question}
            Exclusion or no exclusion? The authors state multiple times that "every process with a positive non-trivial information closure (NTCI) has consciousness." (p.3, and also p.12).
            a) Yet, Figure 4 is ambiguous in the sense that the maximum somehow seems important, while actually all levels should give rise to separate experiences. I don't see how ICT without something like exclusion (IIT style) would indicate that the maximum should correspond to human consciousness. It could just be any one out of many consciousnesses.
            b) p. 14: comparison to IIT: what does ICT say about different sets of variables at the same level. There might well be multiple ways to partition $X$ into S and E, with many overlapping S's. Would those all be conscious? They would not be informationally closed from each other but they could all fulfill the requirements in the Hypothesis. It seems like finding the maximum within a level over the possible sets of elements/variables is a necessary step to identify boundaries (I think also Krakauer does that across sets of variables, but not 100\% sure)        
        \end{question}
    
    	\begin{ans}
            We can see how Figure 4 was ambiguous with respect to this question. We do not impose the exclusion criterion in ICT and have changed Figure 4 to remove the impression that it does. 
            
            Instead of imposing the exclusion criterion, the concept of informational closure itself already involves the notion of individuality and defining the boundary of a system. \citep{BERTSCHINGER.2006}. This allows ICT to solve the individuality problem of consciousness in some cases (but not all; please see the paragraph in Limitations from Line~\lineref{line:individuality}) without imposing an exclusion criterion. Therefore, it is true that Krakauer's boundary detection procedure is potentially helpful and can be adapted for ICT in the future. 
            
            This is also why ICT allows the existence of multiple consciousnesses across the scales of coarse-graining (which IIT does not). Because conscious processes are informationally closed from each other across the scale of coarse-graining, they are not able to know the existence of other consciousnesses within the same system (information flow from other processes is zero). This is in line with using informational closure in level identification \citep{PFANTE.2014}.
            
            We understand that not solving individuality completely is a major weakness of the current version of ICT (and in fact of all IC- and NTIC-based theories). More work on this issue is needed in our future research.
            
    	\end{ans}

        \begin{question}
            Feedback and memory: p. 11. If $NTIC > 0$ is sufficient and true information closure is not required, then feedfoward networks can be conscious according to ICT. Also, in that case, memory is not necessary, as the video camera would have $NTIC > 0$ as long as it records from a stable environment. In that case $I(Y_{t+1}, Y_t) > 0$ and $I(Y_{t+1}, Y_t|E_t)$ is small. This issue here is that having information about the next state does not imply that there is any causation, so if $Y_t$ is highly correlated with $E_t$ and $E_t$ causes $Y_{t+1}$ then NTIC is high. (Thus the IIT emphasis on causation).\\
            If somehow the fact that $Y$ must be informationally closed wrt $X$ does the heavy-lifting here that should be made more explicit (see above).
        \end{question}
        
        \begin{ans}
        	The reviewer is correct. We have reconsidered the case of the feed-forward networks and the video camera example (which can be considered as a single-layer feed-forward network). According to ICT, feed-forward networks can be conscious for deterministic sensor processes. We thank the reviewer for correcting this point. In this case also, a video camera can achieve positive levels of NTIC and, therefore, be conscious. We have worked extensively on Sec.~\ref{sec:causality} and Sec.~\ref{sec:reflexive} to make this clear. In summary, we have mainly revised our manuscript as follows:
        	        	        
        % 	There we have weakened multiple claims in the original version of the manuscript.
        % 	Concerning the camera example we also show that for a camera system filming an environment for which the mutual information from one step to the next is higher than the mutual information between one camera image (sensor values) and the next there are systems that achieve higher NTIC. 
        % 	For the case of the feedforward network we speculate that a similar situation remains true and that there are always systems that achieve higher levels of consciousness than those consisting only of feedforward networks.
        	In summary, we mainly revised our manuscript as follows:
        	\begin{itemize}
        	    \item Added Section \ref{sec:causality} to illustrate two NTIC scenarios about causality. 
        	    \item Added sensory channels in Fig.~2
        	    \item Extensively modified the paragraphs about feed-forward networks and memory in Section 5
        	    \item Added a session in the Appendix to prove that NTIC achieved by modelling the environment can potentially achieve higher NTIC than the one which copies sensory values (e.g., the video camera).
        	\end{itemize}
        	
        	
        	
    %     	Please note that 
        	
		  %  @ The reviewer is correct about the example of the video camera under the condition that the environment past state $E_{t-1}$ shares information with its current state $E_t$, i.e., $I(E_{t-1}, E_t)>0$. 
		    
		  %  @ In such case, simply copying the environmental states to another process (assuming that the sensor of the video camera can capture the whole state of the environment) can lead to positive NTIC. 
		    
		  %  @ This is, in fact, the "Passive adaptation" case mentioned in \cite[p.~4]{BERTSCHINGER.2006},	
		  %  \begin{quote}
			 %     	\textit{"B1)~Passive adaptation: The system is driven by the environment and adapts passively to all changes in the environment. In the case of an environment, that appears deterministic to the system, $H(\hat{e}_{n+1} |\hat{e}_n)=0$, this can be achieved by simply copying the observation of the environment into the system, $S_{n+1} = \hat{e}_n$."}        
		  %  \end{quote} 

	    
	   % @ We can also consider this is a special case of modelling the environment when a system has enough sensory and memory capacities, and, therefore, can virtually model the environment by simply copying the environmental states into the system.  

	   % @ Because this question point to the core concept of ICT, we would like to clarify and emphasise two critical points here. 
	    
	   % @ a) Informational closure and causation: The definition of information closure \citep{BERTSCHINGER.2006} does not involve causation. As described in \cite{BERTSCHINGER.2006}, NTIC can be achieved via "modelling" or "passive adaptation".  In the "modelling" case, the future state of a process ($Y_{t+1}$) can be caused by $Y_t$, which contain predictive information about how the environment influences the system. In the "passive adaptation" case,  the future state of a process ($Y_{t+1}$) is caused by copying environmental information which involves environmental dynamics. 
	    
	   % The latter case may be conceptually counterintuitive because the internal state of the system (e,g, the video camera) is entirely driven by external input. However, it is crucial to know that both cases lead the information flow $J(E\rightarrow Y)$ to (virtually) zero. This means that if $Y_t$ contains information about how the environment $E_t$ causes $Y_{t+1}$, 
	    
	   % However, this is the most critical consequence of solving the scale problem of consciousness in ICT. In physical reality, there only exists microscopic processes at the finest microscopic level. Any causal dependency at coarse-graining levels should be virtual. For example, when $Y$ is informationally closed to X, even though $Y_t$
	    
	   % @ b) As described in our manuscript, to form a higher level of NTIC, the informational richness of the environment, i.e. $H(E)$ also has to be higher since $H(E_t)$ and $H(Y_{t+1})$ both are the upper bound of $I(Y_{t+1}; H(E_t))$. Practically, we believe that with limited sensory and memory capacities, it is difficult to give rise to high NTIC via copying sensory signals to a system. 
	    
        \end{ans}
        
        \begin{question}
            Does ICT imply that one is unconscious while dreaming? In that case $I(Y_{t+1}; Y_t|E)$ should almost be identical to $I(Y_{t+1};I_t)$ and thus lead to NTIC approx. 0.        
        \end{question}
    
    	\begin{ans}
	    	We want to emphasise that not all processes in the neural system are NTIC processes, since some processes in the neural system are not informationally closed.
	    	To the conscious (NTIC) process, the rest of the neural system is considered as part of the environment. This notion is briefly indicated at line \lineref{line:neu-env} in our first version of the manuscript. These processes are still active during sleep and dreaming. We speculate that, during dreaming, the neural system can stably form the NTIC process with respect to its environment, i.e. other parts of the neural system. At present, however, this is mere speculation so we restrained ourself from making the statement in our manuscript. However, we refrained the reviewer for bringing up this important question. This is also an empirical question that can and should be tested in future studies. We believe that this is still worth mentioning. We have added a short paragraph as follows:
	    	
			\addnew{\lineref{line:dream}}{
			Explaining conscious experience during dreaming is always a challenge to theories of consciousness. ICT currently does not have a specific answer to dreaming. However, we wish to emphasize that not all processes in the neural system are NTIC since some processes are not informationally closed. They mainly passively react to sensory inputs or other processes in the neural system. To the conscious (NTIC) process, the rest of the neural system and the body should also be considered as part of the environment. They retain some degree of activity during sleep and dreaming. We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e. the other parts of the neural system. At present, however, this remains mere speculation. Identification of the NTIC process(es) during dreaming is an important milestone in extending the scope of ICT.}
    	\end{ans}
        
        
        \begin{question}
            Minor:
            \begin{enumerate}
                \item "contributions to the field" This section is just a copy paste from the abstract and thus not necessarily helpful. Not sure though what the purpose of this section is meant to be by Frontiers.
                
                \item Introduction: "We currently lack a theory... " IIT and the geometric theory of consciousness (Fekete et al.) have proposed solutions. So there are theories. The following paper should be of interest and should probably be cited:
                Fekete T, van Leeuwen C, Edelman S (2016) System, subsystem, hive: Boundary problems in computational theories of consciousness. Front Psychol 7:1041.
                
                \item $y_t$ corresponds to the content. I would argue that an activation state, without taking the system or relation between elements etc into account is meaningless and cannot capture/explain the structure of an experience. Though this issue can be dealt with at a later time.
            \end{enumerate}
        \end{question}
    
    	\begin{ans}
    		\begin{enumerate}
    			\item In fact we were also confused about this during submission. 
    			We have modified this as follows: \\
    			\textit{"We propose a new theory of consciousness and discuss some preliminary implications."}

    			
    			\item We thank the reviewer for the reminder. We have modified our manuscript and cited the relevant references. 
    			\revise{\lineref{line:lack-theory}}
    			{
    			We currently lack a theory to identify the scale which conscious processes correspond to.
    			}
    			{
    			We currently have only few theories (e.g., Integrated Information Theory \citep{hoel2016can} and Geometric Theory of consciousness \citep{fekete2011towards,fekete2012lack}) to identify the scale which conscious processes correspond to (also see the discussion in \cite{fekete2016system}).
    			}    			
    			
    			\item We agree with the reviewer’s comment. In fact, we do not differentiate states of processes between activation and relation. To take neural networks as an example; : the relations between elements are is determined by the topology of a the network (structure) and its hyperparameters (e.g. activation functions). We agree that the activation and relation of a neural network should be both be considered. After all, they are all of them merely the parameters for the process of the neural network. The only difference between the two groups of the parameters is the temporal scales of changes. States of activation may have more rapid dynamics than states of relation. In ICT, the two sets of parameters do not have any qualitative differences.
    			
    		\end{enumerate}
    		
    	\end{ans}
        
        

\end{document}
